Convergence rate of MAP estimates \\ for the exponential family

### 2021-11-09 aistats.tex
Add meeting notes

\usepackage{aistats/aistats2022}
% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%\usepackage[accepted]{aistats2022}

@@

\aistatsauthor{R\'emi Le Priol \And Frederik Kunstner \And  Damien Scieur \And Simon Lacoste-Julien }

\aistatsaddress{ Mila \And  UBC \And SAIT SAIL \And Mila}
]

@@

As we saw in \S\ref{sec:problem}, MAP  is a special case of stochastic mirror descent (SMD).
This means that \textbf{1)} we may obtain a convergence rate for MAP from an optimization analysis, and \textbf{2)} any insights gained from MAP may inform other designs and analyses of SMD.
In particular, we know that MAP converges asymptotically as $O(n^{-1})$, so we hope to find a convergence rate for SMD that could capture this behavior. 
We first review the assumptions of relative smoothness, helpful to deal with non-smooth functions, before investigating recent analyses of SMD with the MAP.

@@

In this section, we prove the results mentioned in \S\ref{ssec:gaussian-variance},
and add some context and experimental observations.
As mentioned in the main text, the centered gaussian $\cN(0,\sigma^2)$ has sufficient statistic $x^2$ following a Gamma distribution $\Gamma\paren{\half, \inv{2 \sigma^2}}$. 
In this section we derive results for samples  from a general gamma distribution $X \sim\Gamma(\alpha,\beta)$ with known shape parameter $\alpha$, but unknown rate parameter $\beta$.
Results for the Gaussian follow by taking $\alpha=\half$,
 and we also immediately have results for exponential distributions by taking $\alpha=1$.

The density of $\Gamma(\alpha,\beta)$ reads
\alignn{
	p(x) = \frac{\beta^\alpha}{\Gamma(\alpha)} x^{\alpha-1} e^{-\beta x} \; .
}
When $\alpha$ is known, it can be cast as an exponential family~\eqref{eq:def_expfamily} with sufficient statistic $T(x)=x$, domain $\cX = \real_+$ and base measure $\nu(x)\propto x^{\alpha-1}$. Then the natural parameter is $\nat = -\beta < 0$ and the log-partition function is
\alignn{
	\logpart (\nat) = -\alpha \log(-\nat)  + \log\Gamma(\alpha) \; .
}
From there we find that the mean parameter is $\mu = \frac{\alpha}{-\nat} >0$ and the entropy has the same form as the log-partition $\conj(\mu) = - \alpha \log(\mu) + \cst$.
This means that the primal and dual Bregman divergences have the same form as well
\begin{align}
	\bregmanconj(\m_*; \m_n) 
	&= \alpha \left ( \frac{\m_*}{ \m_n} - 1 - \log  \frac{\m_*}{ \m_n} \right) 
	= \alpha \phi\paren{\frac{\m_*}{ \m_n}},
	\\
	\bregman( \nat_n; \nat_* ) 
	&=  \alpha \left ( \frac{ \nat_n}{\nat_*} - 1 - \log  \frac{ \nat_n}{\nat_*} \right)
	= \alpha \phi\paren{\frac{ \nat_n}{\nat_*}},
\end{align}
\begin{wrapfigure}[14]{r}{0.4\textwidth}
	\centering
	\includegraphics[width=.38\textwidth]{phi.pdf}
	\caption{%
	Illustration of $\phi(z)$ (orange) and its upper bound $\phi(z) + \phi\paren{z^{-1}}$ (grey).
	They both are barriers near $0$.
	}
	\label{fig:phi}
\end{wrapfigure}
where these 2 lines are equal, and $\phi$ measures the discrepancy between the ratio $\frac{ \nat_n}{\nat_*} =  \frac{\m_*}{ \m_n}  $ and $1$ via the function
\begin{align}
	\phi(z) := z - 1 - \log(z),
\end{align}
illustrated in orange in Figure~\ref{fig:phi}.
To upper bound for the MAP, due to the difficulty of finding a closed form for the expectation of the logarithm, we focus on the symmetrized Bregman instead
\alignn{
	\bregmanconj( \mu_*; \mu_n) 
	\leq \cS_{\conj} (\mu_*, \mu_n )
	&:= \bregmanconj( \mu_*; \mu_n)  + \bregmanconj( \mu_n; \mu_*) \nonumber\\
	&=  \alpha \paren{\frac{ \mu_*}{\mu_n} -1 +\frac{ \mu_n}{\mu_*} - 1 },
	\label{eq:symmetrized_bregman}
}
which can also be expressed with $\phi$ as follows:
\aligns{
	\label{eq:log_bound}
	\phi(z) \leq \phi(z) + \phi\paren{z^{-1}}
	&=  z -1  + \inv{z} -1
	= \frac{(z-1)^2}{z} \; ,
}
and as illustrated by the grey upper bound in Figure~\ref{fig:phi}.

\subsection{Upper bound for the MLE of the variance}

	\begin{theorem}[MLE Upper Bound]
	For a Gamma $\Gamma(\alpha, \beta)$ with known shape $\alpha$,
	the expected KL between $\mu_*$ and the MLE $\hat\mu_n$	is infinite when $\alpha n\leq 1$ and otherwise upper bounded by
	\begin{align}
		 \expect{\bregmanconj( \mu_*; \hat \mu_n) }
			\leq \inv{2n} + \frac{1}{n(n \alpha-1)}  \; .
	\end{align}
	\end{theorem}

	\begin{proof}
	The MLE is a scaled sum of Gammas $\hat \mu_n = \inv{n} \sum_i X_i$.
	As such it is also a Gamma with parameter $\Gamma(n \alpha, n \beta)$ and expectation $\frac{n\alpha}{n\beta} = \frac{\alpha}{\beta} = \mu_*$.
	If we consider the ratio $\frac{\MAPm}{\mu_*}$, it is also a Gamma with parameter $\Gamma(n \alpha, n \alpha)$ 
	Its inverse follows an inverse gamma distribution with expectation
	\begin{equation}
		\expect{\frac{\mu_*}{\hat \mu_n}} 
		= \begin{cases}
			\frac{n\alpha}{n \alpha -1 }\ \text{ if } n\alpha > 1, \\
			+\infty \  \text{ otherwise. }
		\end{cases}
	\end{equation}
	which implies that for $n\alpha>1$, 
	\begin{align}
		\expect{\frac{\mu_*}{\hat \mu_n}} -1  
		= \frac{n \alpha}{n\alpha -1 } - 1
		= \frac{1}{n \alpha -1}
	\end{align}
	There is also a closed form solution for the expected logarithm of a Gamma.
	Indeed a the sufficient statistic of a Gamma is $(X, \log(X))$, so one can apply formula~\eqref{eq:mirror-map} on the log-partition of a Gamma to get
	\begin{align}
		\expect{\log \frac{\hat \mu_n}{\mu_*}} 
		= \psi\paren{n \alpha} - \log\paren{n \alpha},
	\end{align}
	where $\psi$ is the \href{https://en.wikipedia.org/wiki/Digamma_function}{digamma function.}
	%Closed forms also exist for non-central chi-squares, see for example the note of \citep{pav2015moments}.
	Consequently the suboptimality of the MLE has a closed form solution
	\begin{align}
	\expect{\bregmanconj( \mu_*; \hat \mu_n) }
	&= \alpha \expect{\frac{\mu_*}{ \hat \mu_n} - 1 + \log \left(\frac{\hat \mu_n}{\mu_*} \right) },
	\\
	& =
	\begin{cases}
		\alpha \paren{ \frac{1}{n\alpha - 1} + \psi\paren{n \alpha} - \log\paren{n \alpha} }, \ \text{ if } n\alpha>1, \\
			+\infty \  \text{ otherwise. }
	\end{cases}
	\end{align}
	Surprisingly, for a gaussian variance where $\alpha = \half$, we need $3$ samples or more for the expected loss to be bounded.
	When the expectation is finite, we can get a more interpretable formula using known \href{https://en.wikipedia.org/wiki/Digamma_function#Inequalities}{bounds on the digamma function},
	\begin{align}
		-\inv{x} \leq \psi(x) - \log(x) \leq -\inv{2x} = - \inv{x} + \inv{2x}	\; ,
	\end{align}
	giving, for $n \alpha >1 $,
	\begin{align}
		\frac{\alpha}{n\alpha-1} - \frac{\alpha}{n\alpha}
		&\leq \expect{\bregmanconj( \mu_*; \hat \mu_n) }
		\leq \frac{\alpha}{n\alpha-1} - \frac{\alpha}{n\alpha} + \frac{\alpha}{2n\alpha}
		\\
		\iff
			\frac{1}{n(n \alpha-1)}
			&\leq \expect{\bregmanconj( \mu_*; \hat \mu_n) }
			\leq \inv{2n} + \frac{1}{n(n \alpha-1)} \; ,
	\end{align}
	so we get a $\Omega(n^{-2})$ lower bound and a $O(n^{-1}) + O(n^{-2})$ upper bound.
	\end{proof}

@@

When $n<\inv{\alpha}$, it is possible to get a much tighter bound by exploiting \href{http://dlmf.nist.gov/8.19.E12}{the recurrence relationship} \cite[Eq.~8.19.12]{DLMF}
\alignn{
	\alpha E_{\alpha+1}(\beta) + \beta E_\alpha(\beta) 
	= e^{-\beta} 
}
and combining it with the inequality \citep[Eq.~8.19.21]{DLMF} to get
\alignn{
	\beta e^\beta E_\alpha(\beta)
 	= 1 - \alpha e^\beta E_{\alpha+1}(\beta)
 	\leq 1 - \frac{\alpha}{\alpha + 1 + \beta}
 	 = \frac{\beta + 1}{\alpha + \beta + 1} \; .
}
Plugging this inequality back into~\ref{eq:expect1+gamma}, we get the following upper bound for the MAP:
\alignn{
	\expect{\frac{\mu^*}{\MAPm}} 
	\leq \frac{n_0 + n}{a} \frac{a\alpha + 1}{n \alpha + a \alpha +1}
	= \frac{n_0 + n}{a + n +\inv{\alpha}} \paren{1 + \inv{a \alpha}} \; .
}
Unfortunately, this formula does not yield an elegant convergence rate, so we keep it out of the lemma.

@@

\begin{theorem}[MAP Bound]
The expected symmetrized Bregman~\eqref{eq:symmetrized_bregman} of the MAP of $\Gamma(\alpha, \frac{\alpha}{\mu^*})$ with prior hyper-parameters $(n_0,\mu_0)$ is upper bounded as
\alignn{
    \forall n\geq \inv{\alpha},\quad \quad
	\expect{\cS_\conj(\mu^*, \hat \mu_n)}
	\leq\frac{1}{n_0+n} + 
	\frac{\alpha\paren{\frac{\mu_0}{\mu^*} - \inv{\alpha n_0} - 1 }^2 }{\paren{1+\frac{n}{n_0}}\paren{\frac{\mu_0}{\mu^*} - \inv{\alpha n_0} + \frac{n}{n_0}}}
}
\end{theorem} 
Note that the second term vanishes when $\mu_0 = \mu^* \paren{1 + \inv{\alpha n_0}}$. Expressions for $n\alpha < 1$ are less elegant so we do not write them down here.

@@

\begin{theorem}[MAP Bound]
The expected symmetrized Bregman~\eqref{eq:symmetrized_bregman} of the MAP of $\cN(  0,\m^*)$ with prior hyper-parameters $(n_0,\m_0)$ is upper bounded as
 \begin{align}
	& \expect{\cS_\conj( \m^*; \hat \m_n^\mathrm{MAP})}
	\leq 
	\left\{\begin{array}{ll}
		\cS_\conj( \mu_*; \mu_0) 					& \text{ if } \ n=0, \\
		\inv{2(n_0+1)}  +  b_1 						& \text{ if }\ n=1,\\
		\frac{1}{n_0 \frac{\m_0}{\m^*} +n-2} + b_n  & \text{ if }\ n\geq 2,
	\end{array}\right.
	\quad 
	\quad 
	\text{where }
	b_n = \frac{(1 + \inv{n_0} - \frac{\m_0}{\m^*})^2}{2 (\frac{\m_0}{\m^*}+\frac{(n-2)_+}{n_0})(1 + \frac{n}{n_0} )} \; . 
	%\nonumber
\end{align}
\end{theorem}

@@

>>>>

\usepackage[accepted]{aistats/aistats2022}
% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%\usepackage[accepted]{aistats2022}

@@

\aistatsauthor{R\'emi Le Priol \And Frederik Kunstner \And  Damien Scieur \And Simon Lacoste-Julien \TODO{s} }

\aistatsaddress{ 
	Mila, Université de Montreal 
	\And  University of \\ British Columbia
	\And SAIT AI Lab, Montreal 
	\And Mila, Université de Montreal \\
	Canada CIFAR AI Chair \\
	SAIT AI Lab, Montreal}
]

@@

As we saw in \S\ref{sec:problem}, MAP  can be interpreted as stochastic mirror descent (SMD).
This means that \textbf{1)} we may obtain a convergence rate for MAP from an optimization analysis, and \textbf{2)} any insights gained from MAP may inform other designs and analyses of SMD.
In particular, we know that MAP converges asymptotically as $O(n^{-1})$, so we hope to find a convergence rate for SMD that could capture this behavior. 
We first review the assumptions of relative smoothness, helpful to deal with non-smooth functions, before investigating recent analyses of SMD with the MAP.

@@

In this section, we prove the results mentioned in \S\ref{ssec:gaussian-variance},
and add some context and experimental observations.
As mentioned in the main text, the centered gaussian $\cN(0,\sigma^2)$ has sufficient statistic $T(X)=X^2$ which follows a gamma distribution $\Gamma\paren{\half, \inv{2 \sigma^2}}$. 
MLE and MAP only depend on $T(X)$, not $X$, so their performance only distributions of $T(X)$. 
In this section we derive results for samples  from a general gamma distribution $X \sim \Gamma(\alpha,\beta)$ with known shape parameter $\alpha$, but unknown rate parameter $\beta$.
Results for the Gaussian follow by taking $\alpha=\half$,
 and we also immediately have results for exponential distributions by taking $\alpha=1$.

\begin{theorem}[MLE Upper Bound]
	Consider an exponential family such that $T(X)$ is a gamma $\Gamma(\alpha, \beta)$ with known shape $\alpha$.
	the expected KL between $\mu_*$ and the MLE $\hat\mu_n$	is infinite when $\alpha n\leq 1$ and otherwise upper bounded by
	\begin{align}
		 \expect{\bregmanconj( \mu_*; \hat \mu_n) }
			\leq \inv{2n} + \frac{1}{n(n \alpha-1)}  \; .
	\end{align}
\end{theorem}

This theorem applies to Gaussian variance since 
\TODO{explain how this corresponds to theorem 4.1}

\subsection{Gamma distribution}
The density of $\Gamma(\alpha,\beta)$ reads
\alignn{
	p(x) = \frac{\beta^\alpha}{\Gamma(\alpha)} x^{\alpha-1} e^{-\beta x} \; .
}
When $\alpha$ is known, it can be cast as an exponential family~\eqref{eq:def_expfamily} with sufficient statistic $T(x)=x$, domain $\cX = \real_+$ and base measure $\nu(x)\propto x^{\alpha-1}$. Then the natural parameter is $\nat = -\beta < 0$ and the log-partition function is
\alignn{
	\logpart (\nat) = -\alpha \log(-\nat)  + \log\Gamma(\alpha) \; .
}
From there we find that the mean parameter is $\mu = \frac{\alpha}{-\nat} >0$ and the entropy has the same form as the log-partition $\conj(\mu) = - \alpha \log(\mu) + \cst$.
This means that the primal and dual Bregman divergences have the same form as well
\begin{align}
	\bregmanconj(\m_*; \m_n) 
	&= \alpha \left ( \frac{\m_*}{ \m_n} - 1 - \log  \frac{\m_*}{ \m_n} \right) 
	= \alpha \phi\paren{\frac{\m_*}{ \m_n}},
	\\
	\bregman( \nat_n; \nat_* ) 
	&=  \alpha \left ( \frac{ \nat_n}{\nat_*} - 1 - \log  \frac{ \nat_n}{\nat_*} \right)
	= \alpha \phi\paren{\frac{ \nat_n}{\nat_*}},
\end{align}
\begin{wrapfigure}[14]{r}{0.4\textwidth}
	\centering
	\includegraphics[width=.38\textwidth]{phi.pdf}
	\caption{%
	Illustration of $\phi(z)$ (orange) and its upper bound $\phi(z) + \phi\paren{z^{-1}}$ (grey).
	They both are barriers near $0$.
	}
	\label{fig:phi}
\end{wrapfigure}
where these 2 lines are equal, and $\phi$ measures the discrepancy between the ratio $\frac{ \nat_n}{\nat_*} =  \frac{\m_*}{ \m_n}  $ and $1$ via the function
\begin{align}
	\phi(z) := z - 1 - \log(z),
\end{align}
illustrated in orange in Figure~\ref{fig:phi}.
To upper bound for the MAP, due to the difficulty of finding a closed form for the expectation of the logarithm, we focus on the symmetrized Bregman instead
\alignn{
	\bregmanconj( \mu_*; \mu_n) 
	\leq \cS_{\conj} (\mu_*, \mu_n )
	&:= \bregmanconj( \mu_*; \mu_n)  + \bregmanconj( \mu_n; \mu_*) \nonumber\\
	&=  \alpha \paren{\frac{ \mu_*}{\mu_n} -1 +\frac{ \mu_n}{\mu_*} - 1 },
	\label{eq:symmetrized_bregman} \\
	&= \alpha\phi\paren{\frac{\mu_*}{\mu_n}} + \alpha\phi\paren{\frac{\mu_n}{\mu_*}}
}
Writing $z=\frac{\mu_*}{\mu_n}$ this is equivalent to
\aligns{
	\label{eq:log_bound}
	\phi(z) \leq \phi(z) + \phi\paren{z^{-1}}
	&=  z -1  + \inv{z} -1
	= \frac{(z-1)^2}{z} \; ,
}
and as illustrated by the grey upper bound in Figure~\ref{fig:phi}.

\subsection{Proof for the MLE}

	\begin{proof}
	For gamma distributions, since $T(X)=X$ the MLE is a scaled sum of gammas $\hat \mu_n = \inv{n} \sum_i X_i$.
	As such it is also a Gamma with parameter $\Gamma(n \alpha, n \beta)$ and expectation $\frac{n\alpha}{n\beta} = \frac{\alpha}{\beta} = \mu_*$.
	If we consider the ratio $\frac{\MAPm}{\mu_*}$, it is also a Gamma with parameter $\Gamma(n \alpha, n \alpha)$ 
	Its inverse follows an inverse gamma distribution with expectation
	\begin{equation}
		\expect{\frac{\mu_*}{\hat \mu_n}} 
		= \begin{cases}
			\frac{n\alpha}{n \alpha -1 }\ \text{ if } n\alpha > 1, \\
			+\infty \  \text{ otherwise. }
		\end{cases}
	\end{equation}
	which implies that for $n\alpha>1$, 
	\begin{align}
		\expect{\frac{\mu_*}{\hat \mu_n}} -1  
		= \frac{n \alpha}{n\alpha -1 } - 1
		= \frac{1}{n \alpha -1}
	\end{align}
	There is also a closed form solution for the expected logarithm of a Gamma.
	Indeed a the sufficient statistic of a Gamma is $(X, \log(X))$, so one can apply formula~\eqref{eq:mirror-map} on the log-partition of a Gamma to get
	\begin{align}
		\expect{\log \frac{\hat \mu_n}{\mu_*}} 
		= \psi\paren{n \alpha} - \log\paren{n \alpha},
	\end{align}
	where $\psi$ is the \href{https://en.wikipedia.org/wiki/Digamma_function}{digamma function.}
	%Closed forms also exist for non-central chi-squares, see for example the note of \citep{pav2015moments}.
	Consequently the suboptimality of the MLE has a closed form solution
	\begin{align}
	\expect{\bregmanconj( \mu_*; \hat \mu_n) }
	&= \alpha \expect{\frac{\mu_*}{ \hat \mu_n} - 1 + \log \left(\frac{\hat \mu_n}{\mu_*} \right) },
	\\
	& =
	\begin{cases}
		\alpha \paren{ \frac{1}{n\alpha - 1} + \psi\paren{n \alpha} - \log\paren{n \alpha} }, \ \text{ if } n\alpha>1, \\
			+\infty \  \text{ otherwise. }
	\end{cases}
	\end{align}
	Surprisingly, for a gaussian variance where $\alpha = \half$, we need $3$ samples or more for the expected loss to be bounded.
	When the expectation is finite, we can get a more interpretable formula using known \href{https://en.wikipedia.org/wiki/Digamma_function#Inequalities}{bounds on the digamma function},
	\begin{align}
		-\inv{x} \leq \psi(x) - \log(x) \leq -\inv{2x} = - \inv{x} + \inv{2x}	\; ,
	\end{align}
	giving, for $n \alpha >1 $,
	\begin{align}
		\frac{\alpha}{n\alpha-1} - \frac{\alpha}{n\alpha}
		&\leq \expect{\bregmanconj( \mu_*; \hat \mu_n) }
		\leq \frac{\alpha}{n\alpha-1} - \frac{\alpha}{n\alpha} + \frac{\alpha}{2n\alpha}
		\\
		\iff
			\frac{1}{n(n \alpha-1)}
			&\leq \expect{\bregmanconj( \mu_*; \hat \mu_n) }
			\leq \inv{2n} + \frac{1}{n(n \alpha-1)} \; ,
	\end{align}
	so we get a $\Omega(n^{-2})$ lower bound and a $O(n^{-1}) + O(n^{-2})$ upper bound.
	\end{proof}

@@

When $n<\inv{\alpha}$, it is possible to get a much tighter bound by exploiting \href{http://dlmf.nist.gov/8.19.E12}{the recurrence relationship} \cite[Eq.~8.19.12]{DLMF}
\alignn{
	\alpha E_{\alpha+1}(\beta) + \beta E_\alpha(\beta) 
	= e^{-\beta} 
}
and combining it with the inequality \citep[Eq.~8.19.21]{DLMF} to get
\alignn{
	\beta e^\beta E_\alpha(\beta)
 	= 1 - \alpha e^\beta E_{\alpha+1}(\beta)
 	\leq 1 - \frac{\alpha}{\alpha + 1 + \beta}
 	 = \frac{\beta + 1}{\alpha + \beta + 1} \; .
}
Plugging this inequality back into~\eqref{eq:expect1+gamma}, we get the following upper bound for the MAP:
\alignn{
	\expect{\frac{\mu^*}{\MAPm}} 
	\leq \frac{n_0 + n}{a} \frac{a\alpha + 1}{n \alpha + a \alpha +1}
	= \frac{n_0 + n}{a + n +\inv{\alpha}} \paren{1 + \inv{a \alpha}} \; .
}
Unfortunately, this formula does not yield an elegant convergence rate, so we keep it out of the lemma.

@@

@@

\begin{theorem}[MAP Bound]
The expected symmetrized Bregman~\eqref{eq:symmetrized_bregman} of the MAP of $\cN(  0,\m^*)$ with prior hyper-parameters $(n_0,\m_0)$ is upper bounded as
 \begin{align}
	& \expect{\cS_\conj( \m^*; \hat \m_n^\mathrm{MAP})}
	\leq 
	\left\{\begin{array}{ll}
		\cS_\conj( \mu_*; \mu_0) 					& \text{ if } \ n=0, \\
		\inv{2(n_0+1)}  +  b_1 						& \text{ if }\ n=1,\\
		\frac{1}{n_0 \frac{\m_0}{\m^*} +n-2} + b_n  & \text{ if }\ n\geq 2,
	\end{array}\right.
	\quad 
	\quad 
	\text{where }
	b_n = \frac{(1 + \inv{n_0} - \frac{\m_0}{\m^*})^2}{2 (\frac{\m_0}{\m^*}+\frac{(n-2)_+}{n_0})(1 + \frac{n}{n_0} )} \in O\paren{\frac{n_0^2}{n^2}} \; . 
	%\nonumber
\end{align}
\end{theorem}

@@

\begin{theorem}[MAP Bound]
Consider an exponential distribution with sufficient statistics coming from a gamma distribution $\Gamma(\alpha, \beta^*)$ with mean parameter $\mu^* = \frac{\alpha}{\beta^*}$.
The expected symmetrized Bregman~\eqref{eq:symmetrized_bregman} of the MAP  with prior hyper-parameters $(n_0,\mu_0)$ is upper bounded as
\alignn{
    \forall n\geq \inv{\alpha},\quad \quad
	\expect{\cS_\conj(\mu^*, \hat \mu_n)}
	\leq\frac{1}{n_0+n} + 
	\frac{\alpha\paren{\frac{\mu_0}{\mu^*} - \inv{\alpha n_0} - 1 }^2 }{\paren{1+\frac{n}{n_0}}\paren{\frac{\mu_0}{\mu^*} +  \frac{n - \inv{\alpha}}{n_0}}}
}
\end{theorem} 
Note that the second term vanishes when $\mu_0 = \mu^* \paren{1 + \inv{\alpha n_0}}$.
Expressions for $n\alpha < 1$ are less elegant so we do not write them down here. 
\TODO{try simplification with wolfram alpha}.
